Supplementary Material for Asymmetry paper

### 2020-05-14 Supplementary/Sup_mat.Rmd
Updating gigignore

## Experiment 1: Hoop Size
```{r Load in Hoop size data, inclued = F, echo = F}
load("../Analyses/Experiment_3_Hoop_size/modelling/model_outputs/m1")
load("../Analyses/Experiment_3_Hoop_size/modelling/model_outputs/m1_draws")
```

>>>>

In the analyses below, we use multi-level Bayesian beta regression to model the change in standing position $\phi$ when we 1) use unequal hoop sizes, 2) remove the need to chose between hoops, and 3) provide unequal rewards.

## Experiment 1: Hoop Size
```{r Load in Hoop size data, inclued = F, echo = F, cache=TRUE}
load("../Analyses/Experiment_3_Hoop_size/modelling/model_outputs/m1")
load("../Analyses/Experiment_3_Hoop_size/modelling/model_outputs/m1_draws")
```
